The resurgence of the linear optics \sihui{quantum} interferometer --- recent advances \& applications

### 2018-01-08 paper.tex
Added the experiment of Carolan et al. to Sec. 4 as Fig. 2.

Linear optics play a prominent role in quantum information processing. Photons make fantastic `flying' qubits, and are readily used for quantum communication \cite{bib:Northup14} and quantum key distribution \cite{bib:Lo14}. In 2001, Knill, Laflamme and Milburn (KLM) showed that efficient quantum computing is possible using only linear optical components, that is single photons, beamsplitters, phase shifters and photon counting  \sihui{for spatially encoded qubits \cite{bib:KLM01}. At about the same time, Koashi, Yamamoto, and Imoto essentially came to the same result for polarization-encoded qubits \cite{Koashi01}.} Furthermore, an optical implementation of quantum protocols can potentially piggyback on existing communication infrastructure. Combined with the relative ease of transporting quantum states of light, as compared to say trapped ions or superconducting qubits, linear optics forms a powerful platform for quantum information processing.

@@

\begin{figure}[!htb]
\centering
\includegraphics[width=0.4\columnwidth]{reck}
\caption{Efficient decomposition of arbitrary linear optics networks into a sequence of beamsplitters and phase-shifters. \sihui{This setup describes a generalized multi-port Mach-Zehnder interferometer}} \label{fig:Reck}	
\end{figure}

Alternatively, Mach-Zedner interferometers can also be employed as building blocks instead of beamsplitters and phase-shifters \cite{bib:Englert2001}. Later, it was shown that any nontrivial beamsplitter, that does more than permuting modes or adding phases to them, is universal for linear optics \cite{bib:Bouland2014}. However, they do not provide an explicit construction for arbitrary unitaries.

>>>>

Linear optics play a prominent role in quantum information processing \cite{bib:LovettKok}. Photons make fantastic `flying' qubits, and are readily used for quantum communication \cite{bib:Northup14} and quantum key distribution \cite{bib:Lo14}. In 2001, Knill, Laflamme and Milburn (KLM) showed that efficient quantum computing is possible using only linear optical components, that is single photons, beamsplitters, phase shifters and photon counting  \sihui{for spatially encoded qubits \cite{bib:KLM01}. At about the same time, Koashi, Yamamoto, and Imoto essentially came to the same result for polarization-encoded qubits \cite{Koashi01}.} Furthermore, an optical implementation of quantum protocols can potentially piggyback on existing communication infrastructure. Combined with the relative ease of transporting quantum states of light, as compared to say trapped ions or superconducting qubits, linear optics forms a powerful platform for quantum information processing.

@@

\begin{figure}[!htb]
\centering
\includegraphics[width=0.4\columnwidth]{reck}
\caption{Efficient decomposition of arbitrary linear optics 
networks into a sequence of beamsplitters and phase-shifters. 
\sihui{This setup describes a generalized multi-port Mach-
Zehnder interferometer}} \label{fig:Reck}	
\end{figure}

\begin{figure}[!htb]
\centering
\includegraphics[width=\columnwidth]{configMZI}
\caption{ \sihui{(a) Efficient decomposition of arbitrary linear optics networks into a sequence of beamsplitters and phase-shifters represented as subunitaries, $D_i$. These subunitaries are controlled via their photon amplitudes ($\alpha_{i,j}$) and phases ($\phi_{i,j}$). This setup describes a generalized multi-port Mach-Zehnder interferometer, and is a universal linear-optical processing unit. (b) A state-of-art implementation of a universal linear-optical processing unit is shown. The processor has 6 inputs entering from the left, and 6 outputs leaving to the right, and is constructed from a cascade of 15 Mach-Zehnder interferometers. The classical control and processing unit sets the parameters for the interferometer, and actively cools it. Adapted from \cite{bib:Carolan15}.}} \label{fig:Carolan}	
\end{figure}

Alternatively, Mach-Zedner interferometers can also be employed as building blocks instead of beamsplitters and phase-shifters \cite{bib:Englert2001}. \sihui{Such a decomposition and its implementation on an integrated photonic chip are shown in Fig.~\ref{fig:Carolan}. } Later, it was shown that any nontrivial beamsplitter, that does more than permuting modes or adding phases to them, is universal for linear optics \cite{bib:Bouland2014}. However, they do not provide an explicit construction for arbitrary unitaries.
